### 2020-05-21 writeup/intro.tex
revision

	A crucial technical tool that we develop is the asymptotic limit of the trace of two random matrices.
	The result extends the well-known Marchenko–Pastur law in random matrix theory to the sum of two independent random matrices, which may be of independent interest.

\textbf{How task data affects transfer.}
	We identify three factors: task model similarities and their noise level, data size and covariate shift \cite{PY09,K18}.
	These are achieved through tight generalization bounds established in the high-dimensional regression setting.
	Using these tools, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
	\begin{itemize}
		\item We provide a sharp transition to show that task model similarities can determine whether there is positive transfer.
		For settings where tasks are similar, we further show that the transfer effect depends on the single-task accuracy of the source task.
		\item We show how source task data size can also determine transfer by providing a sharp transition.
		We use our tools to explain the result of taskonomy \cite{ZSSGM18}, regarding the data efficiency of multi-task learning.
		\item Our result has implications on the following question.
	Is it better for two tasks to have the same covariance matrix or complementary covariance matrices.
	For our setting, we show that when the data ratio is large, having the same covariance matrix provably yields the lowest test performance on the target task.
	On the other hand, when data ratio is small, we find that there are cases when having complementary covariance matrices is better.
	The result provides insight into why the covariance alignment algorithm can help improve performance in \cite{WZR20}.
	\end{itemize}

>>>>

	A crucial technical tool that we develop is the asymptotic limit of the trace of the inverse of the sum of two independent sample covariance matrices. Our result not only extends the well-known Marchenko–Pastur law in random matrix theory to the sum of two independent sample covariance matrices with general covariance matrices, but also gives an almost optimal error bound, which may be of independent interest.

\textbf{How task data affects transfer.}
	We identify three factors: task model similarities and their noise level, data size and covariate shift \cite{PY09,K18}.
	These are achieved through tight generalization bounds established in the high-dimensional regression setting.
	Using these tools, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
	\begin{itemize}
		\item We provide a sharp transition to show that task model similarities can determine whether there is positive transfer.
		For settings where tasks are similar, we further show that the transfer effect depends on the single-task accuracy of the source task.
		\item We show how source task data size can also determine transfer by providing a sharp transition.
		We use our tools to explain the result of taskonomy \cite{ZSSGM18}, regarding the data efficiency of multi-task learning.
		\item Our result has implications on the following question.
	Is it better for two tasks to have the same covariance matrix or complementary covariance matrices?
	For our setting, we show that when the data ratio is large, having the same covariance matrix provably yields the lowest test performance on the target task.
	On the other hand, when data ratio is small, we find that there are cases when having complementary covariance matrices is better.
	The result provides insight into why the covariance alignment algorithm can help improve performance in \cite{WZR20}.
	\end{itemize}

### 2020-05-21 writeup/setup.tex
sec 3.1
revision

\subsection{Setup and Main Results}\label{sec_setup}

We assume that for every row $x$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
We will designate the $k$-th task as the target.
Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
Concretely, we focus on the test error for the target task:
%\begin{itemize}
%	\item Estimation error for the target model $\beta_t$: we consider their distance
%		\[ \err(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
		\begin{align*}
			\te_k(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
		\end{align*}
%\end{itemize}

>>>>

\section{Preliminaries}\label{sec_setup}

We assume that for every row $x^\top$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector that has i.i.d. entries with mean $0$ and variance $1$.
We will designate the $k$-th task as the target.
Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
Concretely, we focus on the test error for the target task:
%\begin{itemize}
%	\item Estimation error for the target model $\beta_t$: we consider their distance
%		\[ \err(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
		\begin{align*}
			\te_k(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
		\end{align*}
%\end{itemize}

### 2020-05-21 writeup/technical.tex
minor
intro quick pass
transfer learning
revision

%In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
%We achieve this through tight generalization bounds obtained from random matrix theory.
%For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.
We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
One part captures how similar the task models are and the other part captures the variance of $\hat{\beta}_t^{\MTL}$.
Compared with $\hat{\beta}_t^{\STL}$, we observe that the variance part of $\hat{\beta}_t^{\MTL}$ gets reduced, since more data is added from source tasks.
The bias part of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, affects performance negatively.
We derive the asympotic limit of $\te(\hat{\beta}_t^{\MTL})$ as $p$ approaches infinity.
We compare it with the asympotic limit of $\te(\hat{\beta}_t{\STL})$, for settings where the target data size is limited.
We show sharp generalization bounds for two settings: i) two tasks with general covaraites; ii) many tasks with the same covariates.

@@

For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
\begin{align}
	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
\end{align}
where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
It is not hard to show that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
%The main result of this section show deterministic conditions under which we get positive or negative transfer.
%And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
A key highlight of our approach implies a precise limit on $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}$, which only depends on $\Sigma_1, \Sigma_2$ and $n_1, n_2$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).

\begin{theorem}\label{thm_main_informal}
	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
	Suppose that $n_1 = c_1 p$ and $n_2 = c_2 p$, where $c_1 > ??$ and $c_2 > 3$ are fixed constants.
	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ that only depends on $\set{\hat{v}, M, n_1, n_2, \beta_1, \beta_2}$ such that
	\begin{itemize}
		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $\Delta_{\vari} - \Delta_{\beta} \le \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{theorem}

@@

>>>>

%In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
%We achieve this through tight generalization bounds obtained from random matrix theory.
%For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.
We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
One part captures how similar the task models are and the other part captures the variance of $\hat{\beta}_t^{\MTL}$.
Compared with $\hat{\beta}_t^{\STL}$, we observe that the variance part of $\hat{\beta}_t^{\MTL}$ gets reduced, since more data is added from source tasks.
The bias part of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, affects performance negatively.
We derive the asympotic limit of $\te(\hat{\beta}_t^{\MTL})$ as $p$ approaches infinity.
We compare it with the asympotic limit of $\te(\hat{\beta}_t^{\STL})$, for settings where the target data size is limited.
We show sharp generalization bounds for two settings: i) two tasks with general covaraites; ii) many tasks with the same covariates.

@@

For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
\begin{align}
	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
\end{align}
where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
It is not hard to see that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
%The main result of this section show deterministic conditions under which we get positive or negative transfer.
%And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
A key highlight of our approach implies a precise limit on $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}$, which only depends on $\Sigma_1, \Sigma_2$ and $n_1, n_2$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).

\begin{theorem}\label{thm_main_informal}
	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
	Suppose that $n_1 = c_1 p$ and $n_2 = c_2 p$, where $c_1>1$ and $c_2 >1$ are fixed constants.
	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ and a small deterministic error $\delta$ that only depend on $\set{\hat{v}, M, n_1, n_2, \beta_1, \beta_2}$ such that
	\begin{itemize}
		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $\Delta_{\vari} - \Delta_{\beta} \le \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{theorem}

@@

%\section{Extension to Transfer Learning}

%We study the transfer function of taskonomy \cite{ZSSGM18}.
%The algorithm is as follows.
%First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
%This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
%Then, we learn the output layer on the target task.
%We use our tools to analyze this setting as follows.
%G

### 2020-05-21 writeup/transfer.tex
revision

\begin{example}\label{ex_basic}
	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
	%The noise level for both tasks is equal to $\sigma > 0$.
	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$.
\end{example}

@@

Specifically, the transition threshold is derived in the following proposition.
\begin{proposition}\label{prop_dist_transition}
	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $c_1 > 100$ is a fixed constant.
	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${d^2} < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${d^2} \ge \frac {3\sigma^2} {2p} \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} $, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

@@

\begin{proposition}\label{prop_var_transition}
	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $c_1 > 100$ is a fixed constant and $d^2 < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$. Then we derive the following transition as a parameter of $\sigma_1$:
	\begin{itemize}
		\item If $\sigma_1^2 \le p d^2 \cdot c_1 +\left[1+ \frac23\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)}\right]\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $\sigma_1^2 > p d^2 \cdot c_1 +\left[1+ \frac32\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)}\right] \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

@@

\item If $d^2 > (1 - a^{-1/2})^{-4}\frac{\sigma^2}{p (c_2 - 1)}$, then we have the following transition depending on $c_1$:
		\begin{itemize}
			\item If $c_1 < \frac{(c_2-2)\sigma^2}{(1+a^{-1/2})^4(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
			\item If $c_1 > \frac{(c_2-2) \sigma^2}{(1-a^{-1/2})^4(1-(a+c_2-2)^{-2})(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
		\end{itemize}
	\end{itemize}
\end{proposition}

@@

For this setting, covariate shift is captured by the matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
Our result shows that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix is equal to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.

@@

\begin{proposition}\label{prop_covariate}
	In the setting of Example \ref{ex_basic}, assume that $c_1 > 3$ and $c_2>3$,
and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$. As a parameter of $M \in \cS_{\mu}$, we have that $(\te(\hat{\beta}_t^{\MTL}))(M)$ as a function of $M$ satisfies that 
\be\label{formular_covariate0} (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ C\left(c_2c_1^{-1} + c_1^{-1/2}\right)\right]\cdot\min_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) ,\ee
where the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $C_1$, but otherwise does not depend on $c_1$ and $c_2$. 
	%is minimized when $M = \mu\id$.
\end{proposition}

>>>>

\begin{example}\label{ex_basic}
	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks. For the noises, we assume that $\e_i$ has i.i.d. entries with mean zero and variances $\sigma_i^2$, $i=1,2$. 
	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
	%The noise level for both tasks is equal to $\sigma > 0$.
	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$. For simplicity, we assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in the supplementary material. 
\end{example}

@@

Specifically, the transition threshold is derived in the following proposition.
\begin{proposition}\label{prop_dist_transition}
	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $c_1 > 110$ is a fixed constant.
	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${d^2} < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${d^2} \ge \frac {3\sigma^2} {2p} \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} $, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

Here the constants $\frac23$ and $\frac32$ in this proposition (and the following ones) can be replaced with $(1+c_1^{-1/2})^{-4}$ and $(1-c_1^{-1/2})^{-4}$. In particular, these bounds becomes tighter as $c_1$ increases.

@@

\begin{proposition}\label{prop_var_transition}
	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $c_1 > 110$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$, i.e. we have positive transfer when $\sigma_1=\sigma_2$. Then we derive the following transition as a parameter of $\sigma_1$:
	\begin{itemize}
		\item If $\sigma_1^2 \le p d^2 \cdot c_1 +\left[1+ \frac23\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)}\right]\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $\sigma_1^2 > p d^2 \cdot c_1 +\left[1+ \frac32\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)}\right] \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

@@

\item If $d^2 > (1 - a^{-1/2})^{-4}(1-(a+c_2-2)^{-2})^{-1}\frac{\sigma^2}{p (c_2 - 1)}$, then we have the following transition depending on $c_1$:
		\begin{itemize}
			\item If $c_1 < \frac{(c_2-2)\sigma^2}{(1+a^{-1/2})^4(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
			\item If $c_1 > \frac{(c_2-2) \sigma^2}{(1-a^{-1/2})^4(1-(a+c_2-2)^{-2})(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
		\end{itemize}
	\end{itemize}
\end{proposition}

@@

For this setting, covariate shift is captured by the matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
Our result shows that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.

@@

\begin{proposition}\label{prop_covariate}
	In the setting of Example \ref{ex_basic}, assume that $c_1 > 3$ and $c_2>3$,
and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$. %As a parameter of $M \in \cS_{\mu}$, 
We have that $(\te(\hat{\beta}_t^{\MTL}))(M)$ as a function of $M\in \cS_{\mu}$ satisfies that 
\be\label{formular_covariate0} (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ C\left(c_2c_1^{-1} + c_1^{-1/2}\right)\right]\cdot\min_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) ,\ee
where the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $C_1$, but otherwise does not depend on $c_1$ and $c_2$. 
	%is minimized when $M = \mu\id$.
\end{proposition}
